%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
Accurate temperature prediction holds key significance in distinct sectors, such as power requirements in cities and industry, with deep implications for global climate understanding. This paper presents an innovative approach to enhance temperature prediction through various deep learning(DL) techniques: Long Short-Term Memory (LSTM), Recurrent Neural Networks (RNN), Gated Recurrent Unit (GRU) and Bi-directional Long Short Term Memory (BiLSTM). These DL techniques can capture complex temporal dependencies complements,  modifying overfitting concerns.  The proposed \textbf{Multi-Bidirectional Shifting Based Data Transformation (MBiS-DT)} capitalize on the strengths of traditional (DL) methods, seeking to boost their predictive capability and reduce variance-related errors. Our study adobe into the complex stuff of time-series satellite data, particularly focusing on Delhi city temperature deviation. Informed by the relatively indefinite variation of city temperature, we influence MBiS-DT to get a new shifted dataset. Traditional BiLSTM is introduced, enhancing the predictive power by emphasizing local data interactions.  The BiLSTM methodology performs the best because it adopts a quadratic cost function and strategically weighting training sample data proximate to test different points.
\end{abstract}
