%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
  Time series analysis plays a vital role in medical sciences. It is been of great importance lately to understand the dynamics of data to predict and account for the state of survivability in patients with various conditions. The objective of our work is to understad time series ECG data of patients with certain heart conditions and checking their ECG  prediction error on multiple performance metrics based on Deep learning(DL) models. An array of multichannel ECG recordings were obtained from patients with a variety of cardiac conditions. As the heart's electrical activity over time is recorded,  we gain valuable insight into patient's health. A time series analysis is performed on five patient records since it is a very large database. This is accomplished using advanced DL algorithms significantly used these days for time series analysis (CNN, RNN, LSTM, GRU, BiLSTM). Our Proposed model has a significantly better performance over RMSE,  MSE,  MAE and MAPE upon traditional DL Models. As a result of these findings, The author has demonstrated effectiveness of the proposed approach in predicting the progression of cardiac abnormalities. Health professionals can use these models to make informed decisions and provide timely interventions for patients with cardiac conditions. This study showcases the significance of time series analysis techniques in improving diagnostic capabilities and enhancing patient care in the field of cardiology.
\end{abstract}
