% Chapter Template

\chapter{Conclusion} % Main chapter title

\label{c6} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\section{Conclusion}
Throughout the study, we propose a Mv-XGBr model, and also evaluates its results on ten store sales data. Individually, XGBoost Regressor model is not so much effective comparably with other models discussed in this study. But the proposed methodology brings a remarkable effect in predicting the store sales data. This is the basis of novelty work done in this study. The given results demonstrate that the proposed framework outperforms the discussed models like, AdaBoost Regressor, Catboost Regressor, XGBoost Regressor as well as Extra Tree individually. The Mv-XGBr model is not only effectively applicable in our case, but it can be used on other timeseries datasets belonging to climate, medical, environmental and so on.  
In similar terms, the proposed method can even be implemented with other models as well to bring less error in predicting the test data, as we can see that Extra Tree is relatively performing well and very closed to the proposed method in original datasets. Apart from that, in terms of feature extended of datasets $X’$, the proposed methodology is not working much effectively for the same view as in dataset $X$ for both performance metrices that is, RMSE and MAPE, under same number of views taken under consideration for the original datasets. But this limitation can be eliminated by increasing number of views. Hence, the values of RMSE reduces when view number approaches the length of features. Also, there can be some more effective types of view aggregation techniques while implementing the multi-view concept and that is the matter of extreme analysis and research.The basic behaviour of views in this study are alredy been mentioned in the form of tabular results but there is a further scope of study about the rate of decrease of RMSE and MAPE values relative to the corresponding views number.\\


\textbf{Declaration of Competing Interest}\\
The authors declare that they have no any kind of known financial interest or any kind of personal interest that could influence the work reported in this paper.
%\newpage
%\pagebreak
\textbf{Md. A. Sohail} : Conceptualization, methodology, formal analysis, Resource, Writing original draft, visualization.\\
\textbf{Dr. Vipin Kumar} : methodology, conceptualization, validation, investigation, writing, review editing, supervision.

\subsection*{Data availability}



%The data is available on Kaggle website, with title name "Rossmann Store Sales" data. There are some kaggle competition events are already held in the same data. 



\subsection*{Acknowledgments}

%A heartfelt applause to the Physionet's attempt in making this research possible by providing free clinical records to study cardiovascular diseases by people who have no prior idea about clinical sciences. 