%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
  Sales prediction is one of the most important segments of time series data specially when there
is a multiple store outlet from different locations. Sales data have numerous significance in
world of business and industry because, directly or indirectly it influences human resource as
well as economy of any specified region or country. Time series concept refers to the variation
of data observations relative to time and observed patterns in the data with their significance
within a specified time range. Similar to sales data, there are several other data can be observed
in real world scenario, that varies relative to time. In this study, the author have proposed an
important ML framework that gives important insight about multivariate data. The approach is
all about muti-view learning of different store data by Mv-XGBr model. The paper gives an idea
of different views of multivariate data, with its characteristics and also illustrates the comparative
analysis with other similar kinds of ML models.It is also describes the effect of feature extension
of dataset by different approaches like binning and transformation, followed by implementing
the same given models.The final results of the model describes the dominance of proposed Mv-
XGBr model over other models with exceptional improvements in the results for the given data.
It has been also conducted non-parametric experiment related to model, describing the validity of
model results using Friedman Ranking. one of such models analysis and validation technique
is Friedman Ranking. Friedman ranking concept is discussed and applied to the used models
under different given dataset, and establishes the validity of the proposed framework.
\end{abstract}
